INTELLIGENT SYSTEMS

### 2021-04-11 papers/paper_3.tex
new folders structures

\subsubsection{Experimental Results}
Various quality factors (\emph{QS}), useful for indicating the degree of loss in a 
compressed image, are manually set in order to achieve the same bits per 
pixel (\emph{bpp}) of the original image. In order to compare the other methods 
existing at the state of the art with the proposed method, two compression 
quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5, the ù
comparison results obtained are shown in figure \ref{fig:QF5}, while the results 
obtained whit \emph{QF} set to 10 are shown in figure \ref{fig:QF10}
\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
    \centering
    \caption{JPEG: QF=5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
    \label{fig:QF5}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
    \centering
    \caption{JPEG: QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
    \label{fig:QF10}
\end{figure}

>>>>

\subsubsection{Experimental Results}
Various quality factors (\emph{QS}), useful for indicating the degree of loss in a 
compressed image, are manually set in order to achieve the same bits per 
pixel (\emph{bpp}) of the original image. In order to compare the other methods 
existing at the state of the art with the proposed method, two compression 
quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5 and 10, the 
comparison results obtained are shown in figure \ref{fig:QF5}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
    \centering
    \caption{JPEG: QF=5 and QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
    \label{fig:QF5}
\end{figure}
As we can see from figure \ref{fig:QF5}, 
the most used method in the state of the art \cite{0799924108} blurs the image a lot by 
losing some detail on the corners, the proposed method has a gain of 1.20db 
in PSNR, producing compressed images with better quality, and a gain of 
0.0227 in SSIM indicating a high similarity with the original image. The 
proposed framework also manages to exceed the performance of the ARCNN 
\cite{0799924109} method which represents a milestone in this area. The strength of the 
proposed method is based on obtaining better compression than commonly 
used codecs, such as \emph{JPEG}, \emph{JPEG2000} and \emph{BPG}, in a variable bit rate 
range. As we can see from the comparison made in figure \ref{fig:JPEG2000p}, the difference 
in visual quality between the proposed method and the JPEG2000 codec 
is considerable. With the same amount of bit rates, the JPEG2000 codec 
produces worse results by losing several structural information.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/JPEG2000p.png}
    \centering
    \caption{Performance comparison of JPEG2000 at difference bit rates.}
    \label{fig:JPEG2000p}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper3/JPEG2000.png}
    \centering
    \caption{Average PSNR(dB)/SSIM results of JPEG2000 and the proposed method.}
    \label{fig:JPEG2000}
\end{figure}
As for the BPG codec, 
if used in combination with the ComCNN and RecCNN networks, it reaches 
higher PSNR and SSIM levels than when used individually or with only one 
of the two networks, moreover, on average, it has a saving of about 5.22\% of 
the amount of bit rate.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/BPG.png}
    \centering
    \caption{BPG: PSNR (dB) and SSIM result of BPG, BPG + RecCNN and the proposed method.}
    \label{fig:BPG}
\end{figure}

\subsubsection{Running Time}
The execution time of all algorithms, CPU and GPU, are shown in figure \ref{fig:time}. 
It should be noted that the time reached by the GPU was calculated only 
for the proposed method. The processed images, in grayscale, are in a size 
of 256x256. The proposed algorithm appears to be the fastest compared to 
the others.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/time.png}
    \centering
    \caption{Running time(s) of compared methods in CPU (/GPU) }
    \label{fig:time}
\end{figure}

\subsection{CONCLUSION}
The proposed method seems to have the best performance compared to other 
methods already existing in the state of the art. The proposed technique 
then validates the use of one or more convolutional neural networks to carry 
out the task of encoding and decoding images, even in some cases achieving 
better quality than existing codecs for image compression.

### 2021-04-11 papers/paper_5.tex
new folders structures

\subsection{RELATED WORK}
Some methods have placed inertial sensors in different parts of the body 
such as legs \cite{0857651733}, hips \cite{0857651732}, ankles, or even in objects such as bags [35] and 
pockets \cite{0857651720}. Other methods \cite{0857651736} directly use all the inertial sensors present 
in the smartphone. With the advent of deep learning and CNNs, classifying 
an activity has turned out to be an easier job. The input provided to these 
networks is either the raw data of the inertial sensors, or the images that 
represented such data. The entire sequence of data is divided into segments, 
or windows, in order not to negatively affect the performance of the network. 
In the following work, a union of all the data produced by inertial sensors is 
carried out with the multi-task approach in order to provide a single model 
that uses different inputs to produce different outputs.

>>>>

\subsection{RELATED WORK}
Some methods have placed inertial sensors in different parts of the body 
such as legs \cite{0857651733}, hips \cite{0857651732}, ankles, or even in objects such as bags \cite{0857651735} and 
pockets \cite{0857651720}. Other methods \cite{0857651736} directly use all the inertial sensors present 
in the smartphone. With the advent of deep learning and CNNs, classifying 
an activity has turned out to be an easier job. The input provided to these 
networks is either the raw data of the inertial sensors, or the images that 
represented such data. The entire sequence of data is divided into segments, 
or windows, in order not to negatively affect the performance of the network. 
In the following work, a union of all the data produced by inertial sensors is 
carried out with the multi-task approach in order to provide a single model 
that uses different inputs to produce different outputs.

### 2021-04-11 papers/paper_6.tex
new folders structures

\subsubsection{Semantic Segmentation Results}
\begin{enumerate}
    \item \emph{Impact of the mask quality}: as shown in Table \ref{IoU}, the various processing 
    steps lead to a constant increase in the IoU index. In particular, 
    the value reached by the index is that relating to the first round of 
    network training, therefore we proceed recursively with the training of 
    the network so that it can produce a better mask.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c|c|}
            \hline
            Training Mask Type & IoU(\%)\\
            \hline
            Coarse Masks & 32.5 \\
            Bounding Boxes & 35.2 \\
            Enhanced Masks & 47.7 \\
            Refined Masks & 50.4 \\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{THe performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
        \label{IoU}
    \end{table}

@@

    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Fig. \ref{fig:IoU score comparison}). In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels. The proposed model, on the other hand, while using the image-level labels annotation method, achieves an average IoU score greater than 60\% on both the evaluation and test sets. However, there are several classes in which the model obtains a low IoU value (Fig. \ref{fig:classes}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper6/comparison.png}
        \centering
        \caption{Comparison, in terms of IoU score, between different models.}
        \label{fig:IoU score comparison}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
        \centering
        \caption{Score of IoU in some classes.}
        \label{fig:classes}
    \end{figure}
\end{enumerate}

@@

\subsubsection{Foreground Segmentations Results}

>>>>

\subsubsection{Semantic Segmentation Results}
\begin{enumerate}
    \item \emph{Impact of the mask quality}: as shown in Table \ref{IoU}, the various processing 
    steps lead to a constant increase in the IoU index. In particular, 
    the value reached by the index is that relating to the first round of 
    network training, therefore we proceed recursively with the training of 
    the network so that it can produce a better mask.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c|c|}
            \hline
            Training Mask Type & IoU(\%)\\
            \hline
            Coarse Masks & 32.5 \\
            Bounding Boxes & 35.2 \\
            Enhanced Masks & 47.7 \\
            Refined Masks & 50.4 \\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{The performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU.}
        \label{IoU}
    \end{table}

@@

    \item \emph{Comparison with others}: The performance comparison is carried out on both the validation and test sets of the PASCAL VOC dataset (Tab. \ref{IoU score comparison}). In the state of the art, models trained with methods based on object-level labels annotation obtain a better score (greater than 60\%) than models trained with methods that have an annotation of the type image-level labels. The proposed model, on the other hand, while using the image-level labels annotation method, achieves an average IoU score greater than 60\% on both the evaluation and test sets. However, there are several classes in which the model obtains a low IoU value (Fig. \ref{fig:classes}).
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=0.8\textwidth}
        \begin{tabular}{|c|c|c|}
            \hline
            Methods & mIoU(val) & mIoU(test)\\
            \hline
            Supervision: Object-level Labels & &\\
            SDI \cite{0876055513} & 65.7 & 67.5\\
            \hline
            Supervision: Image-level Labels & &\\
            Bootstrap \cite{0876055555} & 63.0 & 63.9\\
            \bfseries{The proposed weakly supervised method} & \bfseries{61.9} & \bfseries{62.8}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Comparison, in terms of IoU score, between different models.}
        \label{IoU score comparison}
    \end{table}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
        \centering
        \caption{Score of IoU in some classes.}
        \label{fig:classes}
    \end{figure}
\end{enumerate}

@@

\subsubsection{Foreground Segmentations Results}
Also for the segmentation of objects in the foreground, comparisons were 
made with existing models of the state of the art. The dataset used this 
time is that of the MIT Object Discovery unlike the PASCAL VOC used 
in the previous comparisons. From the performance obtained, the proposed 
model, which is remembered to be weakly supervised, manages to achieve the 
performance of the supervised models, with a difference of 2.06\% compared 
to the supervised \emph{PixelObjectness} model \cite{0876055538}.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||c|c|c|c||c|c|c|c|}
        \hline
        \multirow{2}{*}{\bfseries{Methods}} & \multicolumn{4}{c||}{\bfseries{MIT dataset (subset)}} & \multicolumn{4}{c|}{\bfseries{MIT dataset (full)}} \\            & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} \\
        \hline
        \bfseries{\#Images} & 82 & 89 & 93 & N/A & 470 & 1208 & 810 & N/A\\
        \hline
        UnsupervisedSeg \cite{0876055520} & 61.37 & 70.52 & 55.09 &62.32 & N/A & N/A & N/A & N/A\\
        \hline
        PixelObjectness \cite{0876055538} & 66.43 & 85.07 & 60.85 &70.78 & 66.18 & 84.80 & 64.90 & 71.96\\
        \hline 
        \bfseries{FPN-Baseline} & 61.09 & 76.22 & 57.89 & \bfseries{65.08} & 61.93 & 75.94 & 64.03 & \bfseries{67.3}\\
        \hline
        \bfseries{Proposed Method} & 64.92 & 77.60 & 60.36 & \bfseries{67.63(+2.57)} & 65.88 & 77.07 & 65.82 & \bfseries{69.59(+2.29)}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Quantitative Results of Foreground Segmentation on MIT object Discovery Dataset.}
    \label{}
\end{table}

\subsection{CONCLUSION}
The proposed framework is therefore useful for carrying out a semantic segmentation 
starting with the mask, identified by an unsupervised network for 
the identification of objects in the foreground \cite{0876055520}, and then improving it 
with a fully convolution neural network. The final mask is obtained simply 
by training the model with the annotated labels for each category. The 
method also manages to detect multiple masks for each type of category 
present in each image. It is also possible to identify a foreground object, 
achieving performance equivalent to that of supervised methods.
